Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-08-04 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
added fig.cap captions for plots. Also, changed one chunk name to avoid having underscores in figure reference.

```{r, scatter-{{hot_chr}}}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == "{{keller_mediator}}", nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", {{hot_chr}}, "_scatter.svg")
fnpdf <- paste0("Chr", {{hot_chr}}, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

```{r, scatter_by_local-{{hot_chr}}, fig.height = ceiling(nlocal / 2)}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = max(foo$pleiotropy_lod), y = 1, label = local_symbol), inherit.aes=FALSE)

@@

```{r, heat-{{hot_chr}}}
ord <- match(rn, rownames(pm))

@@

```{r, index_v_position-{{hot_chr}}}
bar <- foo %>%
  filter(local_symbol == "{{keller_mediator}}")

>>>>

```{r, scatter-{{hot_chr}}, fig.cap="Pleiotropy test statistic vs. mediation LOD difference for Chr {{hot_chr}} hotspot."}
p <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id) %>%
  ggplot() + geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = local_symbol == "{{keller_mediator}}", nonlocal = nonlocal_symbol, local = local_symbol), size = 0.05) + theme(legend.position = "none") + xlab("Pleiotropy LOD") + ylab("Mediation LOD difference")
fnsvg <- paste0("Chr", {{hot_chr}}, "_scatter.svg")
fnpdf <- paste0("Chr", {{hot_chr}}, "_scatter.pdf")
ggsave(plot = p, filename = here("analysis", "figures", fnsvg))
ggsave(plot = p, filename = here("analysis", "figures", fnpdf))
plotly::ggplotly(p)
```

```{r, scatter_by_local-{{hot_chr}}, fig.height = ceiling(nlocal / 2), fig.cap="Pleiotropy test statistic vs. mediation LOD difference by local expression trait for Chr {{hot_chr}} hotspot."}
foo <- pleio_mixed_list %>%
  bind_rows() %>%
  rename(pleiotropy_lod = lod) %>%
  inner_join(med_tib, by = c("local_gene_id", "nonlocal_gene_id")) %>%
  dplyr::select(local_symbol, nonlocal_symbol, pleiotropy_lod, lod_diff, lod_diff_proportion, lod_without_med, lod_with_med, filename, nonlocal_gene_id, local_gene_id)
p <- foo %>%
  ggplot() +
  geom_point(mapping = aes(x = pleiotropy_lod, y = lod_diff, colour = nonlocal_symbol), size = 0.1) +
  facet_wrap(. ~ local_symbol, nrow = ceiling(nlocal / 2), ncol = 2) +
  broman::karl_theme(strip.placement = "inside") +
  theme(legend.position = "none") +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) +
  xlab("Pleiotropy LOD") +
  ylab("Mediation LOD difference") +
  geom_text(aes(x = max(foo$pleiotropy_lod), y = 1, label = local_symbol), inherit.aes=FALSE)

@@

```{r, heat-{{hot_chr}}, fig.cap="Heatmap for pleiotropy test statsitics for Chr {{hot_chr}}."}
ord <- match(rn, rownames(pm))

@@

```{r, index-v-position-{{hot_chr}}, fig.cap="QTL peak position vs. dendrogram index for Chr {{hot_chr}}."}
bar <- foo %>%
  filter(local_symbol == "{{keller_mediator}}")
